The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-07-29 paper.qmd
made small map changes from meeting

# Choropleth Map
p1a <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = bitemp, 
              geometry = geometry)) + 
  scale_fill_manual(values = basecols) +
  #scale_fill_gradientn(colours = basecols, 
  #                     values=breaks/limits[2],
  #                     limits=limits) +
  theme_void() + 
  theme(legend.position = "none")

@@

show_pal <- function (colours, borders = NULL, cex_label = 1, ncol = NULL, myxlab, breaks) {
  # Set dimensions of palette
  n <- length(colours)
  ncol <- ncol %||% ceiling(sqrt(length(colours)))
  nrow <- ceiling(n/ncol)
  # make matrix with null values (if not full)
  colours <- c(colours, rep(NA, nrow * ncol - length(colours)))
  colours <- matrix(colours, ncol = ncol, byrow = TRUE)
  # set graphical parameters (?)
  old <- par(pty = "s", mar = c(0, 0, 0, 0))
  on.exit(par(old))
  size <- max(dim(colours))
  plot(c(0, size), c(0, -size), type = "n", xlab = "", ylab = "", 
      axes = FALSE)
  rect(col(colours) - 1, -row(colours) + 1, col(colours), -row(colours), 
       col = colours, border = borders)
  text(c(0,col(colours)), -c(1,row(colours))-0.15, breaks, 
              cex = 1, col = "black")
  text(4, -1.55, myxlab ,cex = 1.5, col = "black")
}

@@

# Exceed Prob Map
p2a <- exeed_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = xprob, 
              geometry = geometry)) + 
  scale_fill_manual(values = basecols) +
  theme_void() + 
  theme(legend.position = "none")

@@

# Bivariate maps
p2a <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = biclass, geometry = geometry)) + 
  scale_fill_manual(values = bivariatepal) +
  theme_void() + 
  theme(legend.position = "none")

@@

# Transparency maps
pta <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = biclass, geometry = geometry)) + 
  scale_fill_manual(values = transpal) +
  theme_void() + 
  theme(legend.position = "none")

@@

# VSUP maps
p3a <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = biclass, geometry = geometry)) + 
  scale_fill_manual(values = VSUP) +
  theme_void() + 
  theme(legend.position = "none")

>>>>

# Choropleth Map
p1a <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = bitemp, 
              geometry = geometry), colour=NA) + 
  scale_fill_manual(values = basecols) +
  #scale_fill_gradientn(colours = basecols, 
  #                     values=breaks/limits[2],
  #                     limits=limits) +
  theme_void() + 
  theme(legend.position = "none")

@@

show_pal <- function (colours, borders = NULL, cex_label = 1, ncol = NULL, myxlab, breaks) {
  # Set dimensions of palette
  n <- length(colours)
  ncol <- ncol %||% ceiling(sqrt(length(colours)))
  nrow <- ceiling(n/ncol)
  # make matrix with null values (if not full)
  colours <- c(colours, rep(NA, nrow * ncol - length(colours)))
  colours <- matrix(colours, ncol = ncol, byrow = TRUE)
  # set graphical parameters (?)
  old <- par(pty = "s", mar = c(0, 0, 0, 0))
  on.exit(par(old))
  size <- max(dim(colours))
  plot(c(0, size), c(0, -size), type = "n", xlab = "", ylab = "", 
      axes = FALSE)
  rect(col(colours) - 1, -row(colours) + 1, col(colours), -row(colours), 
       col = colours, border = borders)
  text(c(0,col(colours)) + c(0.2, 0.1, 0,0,0,0,0,-0.1,-0.2), -c(1,row(colours))-0.25, breaks, 
              cex = 1, col = "black")
  text(4, -1.75, myxlab ,cex = 1.5, col = "black")
}

@@

# Exceed Prob Map
p2a <- exeed_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = xprob, 
              geometry = geometry), colour=NA) + 
  scale_fill_manual(values = basecols) +
  theme_void() + 
  theme(legend.position = "none")

@@

# Bivariate maps
p2a <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = biclass, geometry = geometry), colour=NA) + 
  scale_fill_manual(values = bivariatepal) +
  theme_void() + 
  theme(legend.position = "none")

@@

# Transparency maps
pta <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = biclass, geometry = geometry), colour=NA) + 
  scale_fill_manual(values = transpal) +
  theme_void() + 
  theme(legend.position = "none")

@@

# VSUP maps
p3a <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = biclass, geometry = geometry), colour=NA) + 
  scale_fill_manual(values = VSUP) +
  theme_void() + 
  theme(legend.position = "none")
